Data Preparation

### 2019-01-24 Data Preparation.Rmd
clean grade var.
clean grade
changes names of import

## Textual Data
### Course Catalogues
In order to conduct a preliminary topic modeling of course content, we first analyze their description in the course catalogues. The corpus `corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.
```{r import corpus_catalogues, cache = TRUE}
corpus_catalogues <- Corpus(x             = DirSource("Catalogues"),
                            readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```

@@

```{r import corpus_manuals, cache = TRUE}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                         readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```
## Student Data
The tibble `d_transcript` contains the transcript information of students as was provided. It has 40 columns, and rows correspond to a type of grade (e.g. final grade, attendance) per student per course per time they took it.

```{r import d_transcript, cache = TRUE}
d_transcript <- rbind(
  read_csv(
    "Raw Grades/grades1.csv",
    col_types = cols(
      `Program (Abbreviation)` = col_character(),
      `Appraisal Status` = col_character(),
      `Module Booking Reason (Description)` = col_character(),
      `Object name` = col_character(),
      `Start date` = col_character(),
      `End Date` = col_character()
      )
    ),
  read_csv(
    "Raw Grades/grades2.csv",
    col_types = cols(
      `Program (Abbreviation)` = col_character(),
      `Appraisal Status` = col_character(),
      `Module Booking Reason (Description)` = col_character(), 
      `Object name` = col_character(), 
      `Start date` = col_character(), 
      `End Date` = col_character()
      )
    )
  )
```

@@

>>>>

## Textual Data
### Course Catalogues
In order to conduct a preliminary topic modeling of course content, we first analyze their description in the course catalogues. The corpus `corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.
```{r import corpus_catalogues, cache = TRUE}
corpus_catalogues <- Corpus(x             = DirSource("./Input/Catalogues"),
                            readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```

@@

```{r import corpus_manuals, cache = TRUE}
corpus_manuals <- Corpus(x             = DirSource("./Input/Manuals 2017-18"),
                         readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```
## Student Data
The tibble `d_transcript` contains the transcript information of students as was provided. It has 40 columns, and rows correspond to a type of grade (e.g. final grade, attendance) per student per course per time they took it.

```{r import d_transcript, cache = TRUE}
d_transcript <- rbind(
  read_csv(
    "./Input/Raw Grades/grades1.csv",
    col_types = cols(
      `Program (Abbreviation)` = col_character(),
      `Appraisal Status` = col_character(),
      `Module Booking Reason (Description)` = col_character(),
      `Object name` = col_character(),
      `Start date` = col_character(),
      `End Date` = col_character()
      )
    ),
  read_csv(
    "./Input/Raw Grades/grades2.csv",
    col_types = cols(
      `Program (Abbreviation)` = col_character(),
      `Appraisal Status` = col_character(),
      `Module Booking Reason (Description)` = col_character(), 
      `Object name` = col_character(), 
      `Start date` = col_character(), 
      `End Date` = col_character()
      )
    )
  )
```

@@

### Clean Grade Variable

```{r clean grade variable}
d_transcript <- d_transcript %>%
  mutate(Grade = case_when(Grade == "NG"~ "-1",
                           T~ Grade),
          Grade = str_replace(string = Grade, pattern = ",",replace = "."),
         Grade = as.numeric(Grade))
```
